Word learning at the semantics pragmatics interface

### 2020-04-17 paper/supplementary_material.Rmd
reorganize repo and add bda figure to supplement

The goal of this study is to investigate the integration of semantic and pragmatic information during word learning in children between 2 and 5 years of age. As a first step, we replicate earlier work showing that children rely on different forms of pragmatic and semantic information during word learning. In experiment 1, we show that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge. In a second experiment, we show that children make inferences about word meanings based on common ground. In a third experiment, we find that, when combined in one procedure, children are sensitive to the way that the two inferences are aligned.

Next, we introduce a computational framework which we use to formalize the process of how the inferences are integrated. As a part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. We then use the our modelling framework to ask which of these information sources are necessary to predict children's responses in experiment 3.

@@

The experiment was preregistered at https://osf.io/gy37b. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_me.html`.

@@

In experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study). The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?". Children responded by touching one of the objects. The location of the novel object (left or right table) and the animal character were counterbalanced. Each child received 12 trials, one with each familiar object. The novel object also changed from trial to trial. We coded as correct choice if children chose the novel object as the referent of the novel word.

@@

```{r, include = F}
plot_aoa_ratings <- aoa_ratings%>%
  mutate(image = paste("../experiments/kids/images/",item,".png", sep=""))

@@

knitr::kable(me_comp, caption = "Model comparison in experiment 1 based on WAIC scores and weights.", digits = 2, align = "l")
```

@@

The experiment was preregistered at https://osf.io/au5hr. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_novel.html`.

@@

## Experiment 3: Integration

@@

The experiment was preregistered at https://osf.io/4nm8g. The experiment itself can be run by downloading the associated repository and opening the file `experiments/kids/kids_combination.html`.

@@

We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | object) + (age * alignment | agent)`. We pre-registered to include item as a fixed effect in Experiment 3. The corresponding model was too complex to be constrained by the data. Furthermore, as explained in Experiment 1, items were chosen based on their rated age of acquisition. That is, we assumed that they are not necessarily different kinds but that they represent different locations on a distribution of required semantic knowledge. For further model specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).

The estimate for age was reliably positive (*$\beta$* = `r fixef_comb%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). The incongruent condition had a strong negative impact (*$\beta$* = `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q97.5)%>%round(2)`), showing that children differentiated between the two conditions. The interaction term was weakly - though not entirely - negative, suggesting a shallower slope for age in the incongruent condition (*$\beta$* = `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q97.5)%>%round(2)`). A model lacking `object` as a random effect provided a much poorer fit, suggesting substantial variation across objects (see Table \@ref(tab:table4)). Figure \@ref(fig:fig3)B visualizes the model. Taken together, the results show that children responded to the way the two inferences were aligned with one another.

@@

knitr::kable(comb_comp, caption = "Model comparison in experiment 3 based on WAIC scores and weights.", digits = 2, align = "l")
```

@@

The experiments reported above show that children are sensitive to the types of information sources we intended to manipulate. Experiment 1 showed that children of all age groups make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented. Experiment 2 showed that children are sensitive the common ground manipulation we implemented and that this inference increases with age. Finally, experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another. In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when inferences are combined with one another.

@@

The main purpose of the study was to study *how* children integrate different information sources during word learning and how this process develops with age. To do so, we use Bayesian cognitive models of pragmatic reasoning. We first describe an *integration model* which we think best represents the inference and integration processes and then specify how this model captures developmental change. Next, we ask how well this model *predicts* how children integrate information. That is, in a situation in which we know the development trajectories for the mutual exclusivity inference (for a particualr familiar object) as well as for the common ground inference, what can we say about what happens when they are combined. We then test the predictive power of the model by comparing the model predictions to the data from experiment 3. We use formal model comparison methods to test the *integration model* against a range of alternative models.

Finally, we ask how well our model *explains* the way that children integrate the different information sources. For this analysis, we fit the free parameters in the model to all the available data, those from experiment 1 and 2 as well as the integration data from experiment 3. We then compare the model to a range of alternative models that make different assumptions about how information is integrated and how this process develops. This approach answers the question of how we can best explain how children integrate the different information sources.

@@

Our model describes a listener reasoning about the referent referred to by a speaker's utterance. This reasoning is contextualized by the prior probability of each referent $P(r \mid \rho_i)$. This prior probability is a function of the common ground $\rho$ shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later. We assume that the degree to which interactions around objects are integrated into the common ground (and thus change the prior probability of those objects) depends on the child's age $i$.

@@

The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
  Following @Frank2014, we use an implicit uniform prior over referents in the literal listener.
] Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows. We parameterize the  listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1. $\theta = 0$ correspondes to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene. Each of the novel words are assumed to have semantic knowledge of 0. For $\theta \in (0, 1)$, the semantic interpretation function will select the familiar referent with probability $\theta + (1 - \theta)\frac{1}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.^[
  One could also define $\theta$ to directly denote the probability of selecting the familiar~vs.~unfamiliar referent. The model behavior would be the same except for a translation of this parameter. We choose the parametrization described because we find it more intuitive for $\theta$ to represent the degree of semantic knowledge, where 0 semantic knowledge represents a state of complete uncertainty.
] For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the word $j$ (its expected acquisition trajectory) as well as on the child's age $i$.

```{r bda, include = T, fig.align = "center", fig.cap = "tbd."}
#knitr::include_graphics("../graphs/method_overview.png")
```

@@

The model description above points to three potential loci of developmental change: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. Each of theses components is represented by a parameter that plays a particular functional role in the model. We capture developmental change by making these parameters a function of age $i$ for which we estimate a developmental trajectory (intercept and slope in a (logistic-) linear model) for each parameter.

@@

Technically, the item-specific parameters ($\theta_{ij}$) are estimated in the form of a hierarchical regression (mixed-effects) model: $\theta_{ij} = \text{logistic}(\beta^{\theta}_{0, j} + i \cdot \beta^{\theta}_{1, j})$; each word's lexical development trajectory (the intercept $\beta^{\theta}_{0, j}$  and slope $\beta^{\theta}_{1, j}$ of the regression line for each object) is estimated as a deviation from an overall trajectory of vocabulary development. The intercept and slope for each item are sampled from Gaussian distributions with means $\mu^\theta_0, \mu^\theta_1$ and variances $\sigma^\theta_0, \sigma^\theta_1$: $\beta^{\theta}_{0, j} \sim \mathcal{N}(\mu^\theta_0, \sigma^\theta_0)$ and $\beta^{\theta}_{1, j} \sim \mathcal{N}(\mu^\theta_1, \sigma^\theta_1)$.
$\mu^\theta_0$ and $\mu^\theta_1$ represent the overall vocabulary development independent of particular familiar object--label pairings, and $\sigma^\theta_0$ and $\sigma^\theta_1$ represent the overall variability of intercepts and of slopes between items (see Figure \@ref(fig:bda)). For all regression components, intercepts correspond to the knowledge or sensitivity for our youngest age bin: 2-year-olds. For example, $\mu^\theta_0$ represents the average semantic knowledge of our 2-year-olds and $\mu^\theta_1$ represents the growth in semantic knowledge over developmental time. $\sigma^\theta_0$ represents the variability in the semantic knowledge of our items (for the 2-year-olds) and $\sigma^\theta_1$ represents the variability in growth of semantic knowledge across our different items.

@@

Sensitivity to common ground $\rho$ refers to the probability that an object is taken to be the referent of the utterance, before actually hearing the utterance. In our paradigm, common ground takes the form of *discourse novelty*, and $\rho$ captures the salience (or lack thereof) of an object due to its presence or absence in the social interaction that precedes the utterance. Specifically, the pragmatic listener uses the common ground parameter $\rho$ as the prior probability of the discourse-novel (i.e., the referent that was absent in the social interaction that preceded the utterance): In the *congruent* condition, the object in the prior social interaction (i.e., the discourse-familiar object) was the familiar object, and hence, both common ground (discourse novelty) and mutual exclusivity are cues to the same referent; in the *incongruent* condition, the object in the prior social interaction was the novel object, and hence, common ground (discourse-novelty) and mutual exclusitivity are cues to different referents.  
We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects [akhtar1996role; @diesendruck2004two], which we model with a logistic-linear function: $\rho_i = \text{logistic}(\beta^\rho_0 + i \cdot \beta^\rho_1)$.

@@

All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl]. The corresponding model code can be found in the associated online repository (file `webppl/prediction_model.wppl`). To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned. The resulting predictions come in the form of distributions of developmental trajectories for each object in the congruent and the incongruent condition.

@@

In this section we evaluate different models in terms of how well they *predict* information integration. That is, in a situation in which we know the development of the mutual exclusivity inference as well as the common ground inference, we look at each model's ability to predict what happens when the two are combined (combination data from Experiment 3). Investigating "pure" (or, *a priori*) prediction automatically excludes all models which include parameters that need to be fit to the combination data itself (e.g., a heuristic, non-integrating mixture model, described below). To generate *a priori* predictions, we independently estimated the model parameters for semantic knowledge and speaker informativeness based on Experiment 1 and the parameter for common ground sensitivity based on Experiment 2.

To estimate the parameters for semantic knowledge and speaker informativeness, we adapted the model described above to a situation in which both objects (novel and familiar) have equal prior probability (i.e., no common ground information). We used the data from Experiment 1 to then infer the parameters. That is, we inferred the intercepts and slopes for speaker informativeness (linear regression) and semantic knowledge (logistic regression) that generated RSA model predictions to match the responses generated in Experiment 1. To estimate the parameters representing sensitivity to common ground, we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in Experiment 2.

To estimate the parameter distributions, we collected samples from six independent MCMC chains, collecting 150,000 samples from each chain and removing the first 50,000 for burn-in. We excluded samples from one chain because it got stuck on a local maximum which resulted in parameter distributions that were substantially different from the other chains. The model outputs can be found in the following online repository: git large file storage.

Next, we combined the parameters according to the four models described below. Note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in terms of which parameters they included. The models described below are a full model (*integration model*) and three lesioned models, which selectively omit one type of information. The following model comparison therefore asks which types of information are necessary to make good predictions about how information is integrated. All models used age-specific parameters when the parameter was present. We do not compare models that make different assumptions about how information is integrated, since they require additional parameters specific to Experiment 3. We consider the question of alternative integration models in the [explanation](#explanation) section.

@@

The integration model serves as the full model and takes in all available information. That is, it takes in object-specific semantic knowledge, speaker informativeness and common ground sensitivity and combines these components by way of the process described above. Figure \@ref(fig:fig5) visualizes the corresponding model predictions in comparison to the data from Experiment 3.

@@

The first lesioned model takes in speaker informativeness and common ground sensitivity as well as general semantic knowledge (vocabulary development), but omits semantic knowledge that is specific to the familiar objects. We described above that the parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model. In this model, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object-specific variation around this trajectory (random effects). The *no word knowledge* model takes in the overall trajectory for semantic knowledge---represented by $\mu^\theta_0$ and $\mu^\theta_1$---but ignores object-specific variation. Formally, the semantic knowledge for each item is the same: $\theta_{ij} = \mu^\theta_0 +  i \cdot \mu^\theta_1$. That is, the model assumes a listener whose mutual exclusivity inference does not vary depending on the particular familiar object but only depends on the average semantic knowledge.

@@

The last lesion model only takes in the common ground sensitivity. This corresponds to a listener who only focuses on common ground and ignores the identity of the objects on the tables as well as any inferences their semantic knowledge of the familiar objects license. The model predictions therefore correspond to the prior distribution over objects $P(r \mid \rho_i)$.

@@

In this section we explore how we can best explain information integration across development. We explore alternative ways to think about information integration. The *integration model* outlined above operates via Bayesian inference in that the prior probability of a referent (a consequence of the common ground manipulation) is updated via the likelihood of hearing the utterance heard from a speaker, which is used to derive the mutual exclusivity inference. In essence, this model is a multiplicative model because the posterior probability of each referent given the utterance is proportional to the product of the likelihood of a speaker saying that utterance and the prior probability of that referent.

@@

In the *mixture model* the two inferences (common ground and mutual exclusivity) are computed in the same way as in in the *integration model*. Subsequently, they are weighted by the mixture parameter $\phi$:

>>>>

The goal of this study is to investigate the integration of semantic and pragmatic information during word learning in children between 2 and 5 years of age. As a first step, we replicate earlier work showing that children rely on different forms of pragmatic and semantic information during word learning. In Experiment 1, we show that children make a so called mutual exclusivity inference and that this inference depends on children's developing semantic knowledge. In a second experiment, we show that children make inferences about word meanings based on common ground. In a third experiment, we find that, when combined in one procedure, children are sensitive to the way that the two inferences are aligned.

Next, we introduce a computational framework which we use to formalize the process of how the inferences are integrated. As a part of this, we identify three information sources that children consider when making the alleged inferences: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. We then use the our modelling framework to ask which of these information sources are necessary to predict children's responses in Experiment 3.

@@

The experiment was preregistered at https://osf.io/gy37b. The experiment itself can be run by downloading the associated repository and opening the file `experiments/ex1_me.html`.

@@

In Experiment 1, on one table, there was a familiar object, on the other table, there was a novel object (drawn for the purpose of the study). The speaker requested an object by saying "Oh cool, there is a [non-word] on the table, how neat, can you give me the [non-word]?". Children responded by touching one of the objects. The location of the novel object (left or right table) and the animal character were counterbalanced. Each child received 12 trials, one with each familiar object. The novel object also changed from trial to trial. We coded as correct choice if children chose the novel object as the referent of the novel word.

@@

```{r, include = F}
plot_aoa_ratings <- aoa_ratings%>%
  mutate(image = paste("../experiments/images/",item,".png", sep=""))

@@

knitr::kable(me_comp, caption = "Model comparison in Experiment 1 based on WAIC scores and weights.", digits = 2, align = "l")
```

@@

The experiment was preregistered at https://osf.io/au5hr. The experiment itself can be run by downloading the associated repository and opening the file `experiments/ex2_novel.html`.

@@

## Experiment 3: Combination

@@

The experiment was preregistered at https://osf.io/4nm8g. The experiment itself can be run by downloading the associated repository and opening the file `experiments/ex3_combination.html`.

@@

We modeled the trial by trial data in the following way: `correct ~ age * alignment + (alignment | subid) + (age * alignment | object) + (age * alignment | agent)`. We pre-registered to include item as a fixed effect in Experiment 3. However, we chose to model it as a random effect instead because, as explained in Experiment 1, items were chosen based on their rated age of acquisition. That is, we assumed that they are not necessarily different kinds but that they represent different locations on a distribution of required semantic knowledge. For further model specifications see [Experiment 1](#experiment-1-mutual-exclusivity)).

The estimate for age was reliably positive (*$\beta$* = `r fixef_comb%>%filter(term == "age")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age")%>%pull(Q97.5)%>%round(2)`). The incongruent condition had a strong negative impact (*$\beta$* = `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "alignmentincongruent")%>%pull(Q97.5)%>%round(2)`), showing that children showed a weaker mutual exclusivity inference when common ground information pointed to the other object as the referent. Thus, children differentiated between the two alignment conditions. The interaction term was weakly - though not entirely - negative, suggesting a shallower slope for age in the incongruent condition (*$\beta$* = `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Estimate)%>%round(2)`, 95% CrI: `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q2.5)%>%round(2)` - `r fixef_comb%>%filter(term == "age:alignmentincongruent")%>%pull(Q97.5)%>%round(2)`). A model lacking `object` as a random effect provided a much poorer fit, suggesting substantial variation across objects (see Table \@ref(tab:table4)). Figure \@ref(fig:fig3)B visualizes the model. Taken together, the results show that children responded to the way the two inferences were aligned with one another.

@@

knitr::kable(comb_comp, caption = "Model comparison in Experiment 3 based on WAIC scores and weights.", digits = 2, align = "l")
```

@@

The experiments reported above show that children are sensitive to the types of information sources we intended to manipulate. Experiment 1 showed that children of all age groups make a mutual exclusivity inference, that the strength of this inference increases with age and, crucially, that it depends on the type of familiar object that is presented. Experiment 2 showed that children are sensitive to the common ground manipulation we implemented and that this inference increases with age. Finally, Experiment 3 showed that children respond differently depending on how the mutual exclusivity inference and the common ground inference are aligned with one another. In the next section, we use Bayesian cognitive models to address the question of *how* information sources are integrated when inferences are combined with one another.

@@

The main purpose of the study was to study *how* children integrate different information sources during word learning and how this process develops with age. To do so, we use Bayesian cognitive models of pragmatic reasoning. We first describe an **integration model** which we think best represents the inference and integration processes and then specify how this model captures developmental change. Next, we ask how well this model *predicts* how children integrate information. That is, in a situation in which we know the development trajectories for the mutual exclusivity inference (for a particular familiar object) as well as the common ground inference, what can we say about what happens when they are combined. We then test the predictive power of the model by comparing the model predictions to the data from Experiment 3. We use formal model comparison methods to test the **integration model** against a range of alternative models.

Finally, we ask how well our model *explains* the way that children integrate the different information sources. For this analysis, we fit the free parameters in the model to all the available data, those from Experiment 1 and 2 as well as the integration data from Experiment 3. We then compare the model to a range of alternative models that make different assumptions about how information is integrated and how this process develops. This approach answers the question of how we can best explain how children integrate the different information sources.

@@

Our model describes a listener ($P_L$) reasoning about the referent referred to by a speaker's ($P_S$) utterance. This reasoning is contextualized by the prior probability of each referent $P(r \mid \rho_i)$. This prior probability is a function of the common ground $\rho$ shared between speaker and listener in that interacting around the objects changes the probability that they will be referred to later. We assume that the degree to which interactions around objects are integrated into the common ground (and thus change the prior probability of those objects) depends on the child's age $i$.

@@

The informativity of each utterance is given by imagining which referent a literal listener, who interprets words according to their lexicon $\mathcal{L}$, would infer upon hearing the utterance.^[
  Following @frank2014inferring, we use an implicit uniform prior over referents in the literal listener.
] Thus, this reasoning depends on what kind of semantic knowledge (word--object mappings) the speaker thinks the literal listener knows. We parameterize the listener's knowledge of a word's semantics in terms of a semantic knowledge parameter $\theta$, which varies between 0 and 1. $\theta = 0$ correspondes to the state of knowledge for a completely novel word and results in a semantic interpretation function that chooses randomly between the objects in the scene. Each of the novel words are assumed to have semantic knowledge of 0. For $\theta \in (0, 1)$, the semantic interpretation function will select the familiar referent with probability $\theta + (1 - \theta)\frac{1}{2} = \frac{1 + \theta}{2}$; that is, with probability $\theta$, the listener knows the correct meaning of the word (and picks out the correct referent 100\% of the time); with probability $1 - \theta$, the listener does not know the meaning of the word and must guess, picking out the correct referent 50\% of the time.^[
  One could also define $\theta$ to directly denote the probability of selecting the familiar~vs.~unfamiliar referent. The model behavior would be the same except for a translation of this parameter. We choose the parametrization described because we find it more intuitive for $\theta$ to represent the degree of semantic knowledge, where 0 semantic knowledge represents a state of complete uncertainty.
] For familiar objects, semantic knowledge is a function of the degree-of-acquisition of the associated word, which in turn depends upon the word $j$ (its expected acquisition trajectory) as well as on the child's age $i$.

@@

The model description above points to three potential loci of developmental change: semantic knowledge, expectations about speaker informativeness and sensitivity to common ground. Each of theses components is represented by a parameter that plays a particular functional role in the model. We capture developmental change by making these parameters a function of age $i$ for which we estimate a developmental trajectory (intercept and slope in a (logistic-) linear model, see Figure \@ref(fig:bda)).

@@

Technically, the item-specific parameters ($\theta_{ij}$) are estimated in the form of a hierarchical regression (mixed-effects) model: $\theta_{ij} = \text{logistic}(\beta^{\theta}_{0, j} + i \cdot \beta^{\theta}_{1, j})$; each word's lexical development trajectory (the intercept $\beta^{\theta}_{0, j}$  and slope $\beta^{\theta}_{1, j}$ of the regression line for each object) is estimated as a deviation from an overall trajectory of vocabulary development. The intercept and slope for each item are sampled from Gaussian distributions with means $\mu^\theta_0, \mu^\theta_1$ and variances $\sigma^\theta_0, \sigma^\theta_1$: $\beta^{\theta}_{0, j} \sim \mathcal{N}(\mu^\theta_0, \sigma^\theta_0)$ and $\beta^{\theta}_{1, j} \sim \mathcal{N}(\mu^\theta_1, \sigma^\theta_1)$.
$\mu^\theta_0$ and $\mu^\theta_1$ represent the overall vocabulary development independent of particular familiar word--object pairings, and $\sigma^\theta_0$ and $\sigma^\theta_1$ represent the overall variability of intercepts and of slopes between items (see Figure \@ref(fig:bda)). For all regression components, intercepts correspond to the knowledge or sensitivity for our youngest children: 2-year-olds (2.00 years of age). For example, $\mu^\theta_0$ represents the average semantic knowledge of a 2-year-old and $\mu^\theta_1$ represents the growth in semantic knowledge over developmental time. $\sigma^\theta_0$ represents the variability in the semantic knowledge of our items (for a 2-year-old) and $\sigma^\theta_1$ represents the variability in growth of semantic knowledge across our different items.

@@

Sensitivity to common ground $\rho$ refers to the probability that an object is taken to be the referent of the utterance, before actually hearing the utterance. In our paradigm, common ground takes the form of *discourse novelty*, and $\rho$ captures the salience (or lack thereof) of an object due to its presence or absence in the social interaction that precedes the utterance (see \@ref(fig:fig1)B). Specifically, the pragmatic listener uses the common ground parameter $\rho$ as the prior probability of the discourse-novel (i.e., the referent that was absent in the social interaction that preceded the utterance): In the *congruent* condition, the object in the prior social interaction (i.e., the discourse-familiar object) was the familiar object, and hence, both common ground (discourse novelty) and mutual exclusivity are cues to the same referent; in the *incongruent* condition, the object in the prior social interaction was the novel object, and hence, common ground (discourse-novelty) and mutual exclusitivity are cues to different referents (see Figure \@ref(fig:fig1)C).  
We expect children at different ages to respond differently to the common ground manipulation, resulting in an age specific prior distribution over objects [@akhtar1996role; @diesendruck2004two], which we model with a logistic-linear function: $\rho_i = \text{logistic}(\beta^\rho_0 + i \cdot \beta^\rho_1)$.

```{r bda, engine='tikz', echo = F,fig.align = "center", fig.cap = "Graphical model representing the Bayesian data analysis for **integration model** used for *Explanation*. $L_1$ represents the RSA model defined by Eq. X, used to predict the Combination Data $d^{CM}$  from Expt. 3 for each unique age bin $i$, lexical item $j$, and alignment condition $k$. This RSA model takes as input a speaker optimality parameter $\\alpha_i$ (which varies by age), a semantic knowledge parameter $\\theta_{ij}$ (which varies by age and item), and a common ground sensitivity $\\rho_i$ (which varies by age). Speaker optimality and semantic knowledge parameters are additionally constrained by the data from the Mutual Exclusivity task ($d^{ME}$; Expt. 1), via the same RSA model with no common ground $L'_1$;  common ground sensitivity parameters $\\rho_i$ are directly constrained by the data from the Common Ground experiment ($d^{CG}$; Expt. 2). Each of these RSA parameters is sampled from a linear or logistic regression model that track developmental change (with intercepts and slopes given by $\beta_0$ and $\\beta_1$, respectively). Additionally, the semantic knowledge parameters for individual items $j$ are sampled from global vocabulary developmental parameters $\\mu$ and $sigma$ that characterize the mean and standard deviation of the intercepts and slopes for individual item trajectories."}

\usetikzlibrary{bayesnet}

\begin{tikzpicture}
%% RSA nodes and data
\node[obs](data_comb){$d^{CM}_{ijk}$};
\node[obs, xshift=-3cm, yshift=0cm](data_me){$d^{ME}_{ij}$};
\node[obs, xshift=3cm,  yshift=0cm](data_cg){$d^{CG}_{i}$};

\node[det, above=of data_me](L1_me){$L'_1$};
\node[det, above=of data_comb](L1_comb){$L_1$};
\node[det, above=of L1_comb, xshift=-1.5cm, yshift=-0.5cm](RSA){$RSA$};

\edge{L1_me}{data_me};
\edge{L1_comb}{data_comb};
\edge{RSA}{L1_me};
\edge{RSA}{L1_comb};

% COMMON GROUND
\node[det, above=of data_cg, yshift=0.1cm](rho){$\rho_i$};
\node[latent, right=of rho, yshift=0.5cm](beta_rho_int){$\beta^{\rho}_0$};
\node[latent, right=of rho, yshift=-0.5cm](beta_rho_slope){$\beta^{\rho}_1$};

\edge{rho}{data_cg};
\edge{beta_rho_int}{rho};
\edge{beta_rho_slope}{rho};
\edge{rho}{L1_comb};

%% SPEAKER INFORMATIVITY

\node[det, left=of RSA, xshift=-1cm](alpha){$\alpha_i$};
\node[latent, left=of alpha, yshift=0.5cm](beta_alpha_int){$\beta^{\alpha}_0$};
\node[latent, left=of alpha, yshift=-0.5cm](beta_alpha_slope){$\beta^{\alpha}_1$};

%	\edge{alpha}{L1_me};
\edge{beta_alpha_int}{alpha};
\edge{beta_alpha_slope}{alpha};
\edge{alpha}{RSA};

%% SEMANTIC KNOWLEDGE model

	\node[det, above=of RSA, yshift=-0.25cm](theta){$\theta_{ij}$};
\node[latent, above=of theta, xshift=-1.25cm, yshift=-0.5cm](beta_theta_int){$\beta^{\theta}_{0, j}$};
\node[latent, above=of theta, xshift=1.25cm, yshift=-0.5cm](beta_theta_slope){$\beta^{\theta}_{1, j}$};

\node[latent, above=of beta_theta_int, xshift=-0.5cm](mu_theta_int){$\mu^{\theta}_{0}$};
\node[latent, above=of beta_theta_int, xshift=0.5cm](sigma_theta_int){$\sigma^{\theta}_{0}$};

\node[latent, above=of beta_theta_slope, xshift=-0.5cm](mu_theta_slope){$\mu^{\theta}_{1}$};
\node[latent, above=of beta_theta_slope, xshift=0.5cm](sigma_theta_slope){$\sigma^{\theta}_{1}$};

\edge{theta}{RSA};
%	\edge{theta}{L1_comb};
\edge{beta_theta_int}{theta};
\edge{beta_theta_slope}{theta};
\edge{mu_theta_int}{beta_theta_int};
\edge{sigma_theta_int}{beta_theta_int};
\edge{mu_theta_slope}{beta_theta_slope};
\edge{sigma_theta_slope}{beta_theta_slope};

%	\plate{plate_data_me}{
%		(data_me)
%	}{$i \in \mathcal{P}_{1}$}

%	\plate{plate_data_cg}{
%		(data_cg)
%	}{$i \in \mathcal{P}_{2}$}

\plate{plate_condition}{(data_comb)(L1_comb)}{$k \in \text{alignments}$};

	\plate{plate_items}{
%		(plate_data_me)
%		(plate_data_comb)
%		(plate_condition)
(plate_condition)
	(data_comb)
	(data_me)
	(L1_me)
	(L1_comb)
	(theta)
	(beta_theta_int)
	(beta_theta_slope)
}{$j \in \text{items}$}

	\plate{plate_data_comb}{
	(data_comb)
	(data_cg)
	(data_me)
	(plate_condition)
	(rho)
	(theta)
	(alpha)
	(L1_me)
	(L1_comb)
%		(plate_items)
	}{$i \in \text{2-to-4 year olds}$}

\end{tikzpicture}

@@

All Bayesian cognitive models were implemented in the probabilistic programming language `WebPPL` [@dippl]. The corresponding model code can be found in the associated online repository (file `webppl/prediction_model.wppl`). To generate model predictions, we estimated age sensitive parameter distributions for semantic knowledge (by familiar object), speaker informativeness and sensitivity to common ground and then passed them through the model in line with the different ways in which they can be combined and aligned (Figure \@ref(fig:bda)). The resulting predictions come in the form of distributions of developmental trajectories for each familiar object in the congruent and the incongruent condition.

@@

In this section we evaluate different models in terms of how well they *predict* information integration. That is, in a situation in which we know the development of the (object specific) mutual exclusivity inference as well as the common ground inference, we look at each model's ability to predict what happens when the two are combined (combination data from Experiment 3). Investigating "pure" (or, *a priori*) prediction automatically excludes all models which include parameters that need to be fit to the combination data itself (e.g., a heuristic, non-integrating mixture model, described below). To generate *a priori* predictions, we independently estimated the model parameters for semantic knowledge and speaker informativeness based on Experiment 1 and the parameter for common ground sensitivity based on Experiment 2.

To estimate the parameters for semantic knowledge and speaker informativeness, we adapted the model described above to a situation in which both objects (novel and familiar) have equal prior probability (i.e., no common ground information). We used the data from Experiment 1 to then infer the parameters. That is, we inferred the intercepts and slopes for speaker informativeness (linear regression) and semantic knowledge (logistic regression) that generated RSA model predictions to match the responses generated in Experiment 1. To estimate the parameters representing sensitivity to common ground, we used a simple logistic regression to infer which combination of intercept and slope would generate predictions that corresponded to the average proportion of correct responses measured in Experiment 2. Figure \@ref(fig:bda) visualizes how parameters were estimated.

To estimate the parameter distributions, we collected samples from six independent MCMC chains, collecting 150,000 samples from each chain and removing the first 50,000 for burn-in. We excluded samples from one chain because it got stuck on a local maximum which resulted in parameter distributions that were substantially different from the other chains. The model outputs can be found in the following online repository: XXXXXX.

Next, we combined the parameters according to the four models described below. Note that the parameter distributions were the same for all models (see Figure \@ref(fig:fig4)) and that models only differed in terms of which parameters they included. The models described below are a full model (**integration model**) and three lesioned models, which selectively omit one type of information. The following model comparison therefore asks which types of information are necessary to make good predictions about how information is integrated. All models used age-specific parameters when the parameter was present. We do not compare models that make different assumptions about how information is integrated, since they require additional parameters specific to Experiment 3. We consider the question of alternative integration models in the [explanation](#explanation) section.

@@

The **integration model** serves as the full model and takes in all available information. That is, it takes in object-specific semantic knowledge, speaker informativeness and common ground sensitivity and combines these components by way of the process described above. Figure \@ref(fig:fig5) visualizes the corresponding model predictions in comparison to the data from Experiment 3.

@@

The first lesioned model takes in speaker informativeness and common ground sensitivity as well as general semantic knowledge (vocabulary development), but omits semantic knowledge that is specific to the familiar objects. We described above that the parameters for semantic knowledge are fitted via a hierarchical regression (mixed effects) model. In this model, there is an overall developmental trajectory for semantic knowledge (main effect) and then there is object-specific variation around this trajectory (random effects). The **no word knowledge model** takes in the overall trajectory for semantic knowledge---represented by $\mu^\theta_0$ and $\mu^\theta_1$---but ignores object-specific variation. Formally, the semantic knowledge for each item is the same: $\theta_{ij} = \mu^\theta_0 +  i \cdot \mu^\theta_1$. That is, the model assumes a listener whose mutual exclusivity inference does not vary depending on the particular familiar object but only depends on the average semantic knowledge.

@@

The last lesioned model only takes in the common ground sensitivity. This corresponds to a listener who only focuses on common ground and ignores the identity of the objects on the tables as well as any inferences their semantic knowledge of the familiar objects license. The model predictions therefore correspond to the prior distribution over objects $P(r \mid \rho_i)$.

@@

In this section we explore how we can best explain information integration across development. We explore alternative ways to think about information integration. The **integration model** outlined above operates via Bayesian inference in that the prior probability of a referent (a consequence of the common ground manipulation) is updated via the likelihood of hearing the utterance heard from a speaker, which is used to derive the mutual exclusivity inference. In essence, this model is a multiplicative model because the posterior probability of each referent given the utterance is proportional to the product of the likelihood of a speaker saying that utterance and the prior probability of that referent.

@@

In the **mixture model** the two inferences (common ground and mutual exclusivity) are computed in the same way as in in the **integration model**. Subsequently, they are weighted by the mixture parameter $\phi$:
